Analysis of split plot design using MCMCglmm

### 2020-07-07 README.Rmd
Clean up README

M. Noel

@@

This repository is organized as an R package.
There are a few R functions in this package that were used to generate some of the diagnostic plots related to the analysis.
However, for the most part I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much
about how to organise the files.

@@

    docker run -dp 8787:8787 adamhsparks/rice_AWD_ShB_analysis

@@

Once logged in, use the Files pane (bottom right) open the folder for this project, and open the `.Rproj` file for this project.
Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R
markdown document, and knit them to produce the results in the paper.
More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org)
[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

@@

I used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu 17.10.
See the colophon section of the docx file in `analysis/paper` for a full list of the packages that this project depends on.

>>>>

Michael Noel

@@

This repository is organized as an R package.
Mostly I used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much about how to organise the files.

@@

    docker run -dp 8787:8787 adamhsparks/rice-awd-shb

@@

Once logged in, use the Files pane (bottom right) open the folder for this project, and open the `.Rproj` file for this project.
Once that's open, you'll see the `analysis/paper` directory in the "Files" pane where you can find the Rmarkdown document, and knit it to produce the results in the paper.
More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org)
[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

@@

I used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS.
See the colophon section of the docx file in `analysis/paper` for a full list of the packages that this project depends on.
